---
title: 'Auxilliary analysis: Functional regression'
author: "Mariella Gregorich"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  bookdown::html_document2:
    css: "css_style.css"
    theme: cosmo
    number_sections: true
    keep_md: no
    fig_caption: true
    code_folding: hide
    toc: true
    toc_depth: 2
    toc_float: 
      collapsed: true
      smooth_scroll: true
    highlight: tango
bibliography: ..\\references.bib 
---



```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = F, warning=F, message=F)
pacman::p_load(mvtnorm, igraph, NetworkToolbox, Rcpp, RcppEigen, MASS, lqmm, ggplot2, gridExtra,
               stringr, future.apply, parallel, dplyr, tidyr, knitr, reshape2,kableExtra,
               rmarkdown, bookdown, forcats, rmdformats, refund.shiny, fields)
set.seed(1234)
source("../x_functions.R")
source("../x_setup.R")
source("../01_data_generation.R")

```

# Background

Here, we are interested in functional regression, in partical scalar-on-function (SOF) regression. The R package refund* - REgression with FUNctional Data - includes functions and computational methods for “scalar-on-function” regression: y ∼ x(s). 

The generalized functional linear model for linear regression that relates the outcome $Y_i$ of individual $i$ to a functional covariate $X_i(t)$ can be written as
$$ Y_i \sim N(\mu_i,\eta) $$
$$ \mu_i=\alpha + \int_0^1 X_i(s)\beta(s)ds$$
However, $X_i(t)$ will only ever be observed on a grid rather than be truly functional.

The coefficient function $\beta(t)$ is modeled using a spline basis $\phi(t)=\{\phi_1(t),...,\phi_K(t)\}$,
$$\beta(t)=\sum_{k=1}^K b_k\phi_k(t)= \boldsymbol{\phi}(t)\boldsymbol{b} $$
Thus,
$$ g(\mu_i)=\alpha + \int_0^1 X_i(s)\boldsymbol{\phi}(s)\boldsymbol{b}~ds$$


The coefficient function $\beta(.)$ is a smooth weighting scheme which, when applied to the individual-specific predictors $X_i(.)$, is
most predictive of the outcome. Weights close to zero de-emphasize indiviual-level areas that are not predictive of the outcome, while large relative weights emphasize areas of the curve that are most predictive of the outcome @goldsmith2011penalized.

<br>

# Data generation

In the data generation of the individual-specific networks, a weight-based approach is currently used in which all edge weights of the networks below a threshold of \tau are set to 0. The threshold $\tau$ is currently set to `r sparams$thresh`.

A more realistic implementation would be to choose a separate threshold $\tau_i \in [0,1]$ for each individual-specific network.

```{r}
## ----------- Parameters -------------------------

df.sparams <- data.frame("Terms"=c("Sample size", "Nodes",  "Possible edges","Latent processes","Density of the mean network"),
                         "Values"=c(n,p,po,q,round_0(sum(omega.imat!=0)/po*100,2)))
df.sparams  %>%
  kbl(caption="Parameters for the data-generating mechanism", escape = F) %>%
  kable_classic(full_width = T, html_font = "Calibri")%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T, position = "left",fixed_thead = T)
```



```{r, echo=F, warning=F, message=F}
df <- generate_data(n=sparams$n, p=sparams$p, q=sparams$q, mu=sparams$mu, alpha=sparams$alpha, delta=sparams$delta, 
                    distr.params = distr.params,eta.params=eta.params,
                    beta0=sparams$beta0,xbeta=sparams$xbeta, gbeta = sparams$gbeta, eps=0.2)

data.network <- df[,paste0("GE.",1:po)]
df$Subj <- 1:sparams$n

# Graph-theoretical feature computation for threshold sequence
list.gvars <- lapply(1:nrow(data.network), function(x) 
  data.frame("Subj"=x, wrapperThresholding(eweights=data.network[x,], msize=p, tseq=thresh.seq)))
data.gvars <- data.frame((do.call(rbind, list.gvars)))

# Add outcome Y
data.gvars <- merge(df[,c("Subj","Y")], data.gvars, by="Subj") %>%
  mutate(Value=ifelse(is.nan(Value), NA, Value)) 
```


<br>

```{r, fig.align='center', fig.width=8, fig.height=5, fig.cap="Distribution of the predictor function obtained through varying sparsification and thresholding techniques. The red line indicates the average behaviour of the invidual-specific functional covariate."}
tmp <- data.gvars %>% 
  filter(Variable %in% "cc") %>%
  dplyr::select(Subj,SparsMethod, ThreshMethod, Thresh, Value) %>%
  group_by(Thresh, SparsMethod, ThreshMethod) %>%
  summarise(Value = mean(Value)) %>%
  mutate(Subj=0)

data.gvars %>% 
  filter(Variable %in% "cc") %>%
  ggplot(aes(x=Thresh, y=Value, group=Subj)) +
  geom_line(col="gray80") +
  geom_line(data = tmp, col="red3") +
  scale_x_continuous("Threshold") +
  scale_y_continuous("Clustering coefficient") +
  ggtitle("Individual-specific network analysis") +
  facet_grid(SparsMethod ~ThreshMethod) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5), text = element_text(size=14))

```


```{r, fig.align='center', fig.width=8, fig.height=5, fig.cap="Distribution of the scalar (outcome) and the function (predictor)"}
data.gvars %>%
  dplyr::select(Subj, Y) %>%
  distinct(Y, keep.all=T) %>%
  ggplot(aes(x=Y))+
  geom_histogram(col="black", fill="gray80") +
  ggtitle("Histogram of the outcome Y") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5), text = element_text(size=14))
```


<br>

# Functional regression
[Refund-Package](https://cran.r-project.org/web/packages/refund/refund.pdf) 

[Smoothing terms for the functional covariate](https://stat.ethz.ch/R-manual/R-devel/library/mgcv/html/smooth.terms.html)



```{r}
list.fit.fda <- list()
i=1
for(sm in unique(data.gvars$SparsMethod)){
  for(tm in unique(data.gvars$ThreshMethod)){
    data.FDA <- data.gvars %>%
      filter(Variable %in% "cc" & SparsMethod %in% sm & ThreshMethod %in% tm) %>%
      pivot_wider(values_from = Value, names_from = Thresh) %>%
      select(!(Variable:SparsMethod))
      
    flength=length(thresh.seq)
    data.FDA$X <- as.matrix(data.FDA[,(ncol(data.FDA)-flength+1):ncol(data.FDA)])
    data.FDA <- data.FDA %>% 
      dplyr::select(Subj,Y,X)
    
    list.fit.fda[[i]] <- list("SparsMethod"=sm, "ThreshMethod"=tm, 
                              "fit"=refund::pfr(Y ~ lf(X, k = 5, bs="ps"), method="REML", data=data.FDA, family="gaussian"))
    i=i+1
  }
}
```


```{r, echo=T}
head(data.FDA)
```

<br>

```{r, echo=T, fig.align='center', fig.width=8, fig.height=5, fig.cap="Beta coefficient funcion from functional regression model"}
list.fda.coef <- list()
for(j in 1:length(list.fit.fda)){
  coef <- coef(list.fit.fda[[j]][[3]])
  coef$value.lo <- coef$value - 1.96*coef$se
  coef$value.up <- coef$value + 1.96*coef$se
  list.fda.coef[[j]] <- data.frame("SparsMethod"=list.fit.fda[[j]]$SparsMethod, 
                          "ThreshMethod"=list.fit.fda[[j]]$ThreshMethod, 
                          coef)
}
data.coef <- do.call(rbind, list.fda.coef) 
  
ggplot(data.coef, aes(x=X.argvals, y=value))+
  geom_line() +
  geom_ribbon(ggplot2::aes(ymin = value.lo, ymax = value.up), alpha = 0.1) +
  scale_x_continuous("Threshold", breaks=seq(0,1,0.2)) +
  scale_y_continuous("Estimated coefficient function beta(t)") +
  theme_bw() +
  facet_grid(SparsMethod~ThreshMethod, scales="free_y")
```


<br>

Example of a summary output using the following approach: 

- Sparsification method = `r list.fit.fda[[1]]$SparsMethod`
- Threshold method = `r list.fit.fda[[1]]$ThreshMethod`

```{r, echo=T}
summary(list.fit.fda[[1]][[3]])
```

<br>

```{r, fig.align='center', fig.width=8, fig.height=6, fig.cap="Calibration plot"}
list.fda.pred <- list()
j=1
for(j in 1:length(list.fit.fda)){
  yhat <- list.fit.fda[[j]][[3]]$fitted.values
  y <- list.fit.fda[[j]][[3]]$model$Y
  list.fda.pred[[j]] <- data.frame("SparsMethod"=list.fit.fda[[j]]$SparsMethod, 
                          "ThreshMethod"=list.fit.fda[[j]]$ThreshMethod, 
                          "Y"=y, "Yhat"=yhat)
}
data.pred <- do.call(rbind, list.fda.pred) 

# Calibration
data.pred %>%
  ggplot(aes(x=Y, y=Yhat))+
  geom_point(shape=1) + 
  geom_abline(intercept = 0, col="red3") +
  theme_bw() +
  facet_grid(SparsMethod~ThreshMethod, scales="free_y")
  
```

<br>

```{r}
list.fda.perf <- list()
j=1
for(j in 1:length(list.fit.fda)){
  r.sq <- summary(list.fit.fda[[j]][[3]])$r.sq
  yhat <- list.fit.fda[[j]][[3]]$fitted.values
  y <- list.fit.fda[[j]][[3]]$model$Y
  rmse <- calc_rmse(y, yhat)
  cs <- calc_cs(y,yhat)
  list.fda.perf[[j]] <- data.frame("SparsMethod"=list.fit.fda[[j]]$SparsMethod, 
                          "ThreshMethod"=list.fit.fda[[j]]$ThreshMethod, 
                          "R2"=r.sq, "RMSE"=rmse, "CS"=cs)
}
data.perf <- do.call(rbind, list.fda.perf) 
row.names(data.perf) <- NULL

data.perf %>%
  mutate_at(3:5, round_0, digits=3) %>%
  kbl(caption="Performance of the functional data approach", escape = F) %>%
  row_spec(0, bold=T) %>%
  kable_classic(full_width = T, html_font = "Calibri")%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T, position = "left",fixed_thead = T)

```
<br>

# Best RMSE approach
The bRMSE-approach fits a univariable linear regression model for each sparsification method (SparsMethod $\in$ {density-base, weight-based}), each thresholding method (ThreshMethod $\in$ {trim, bin, resh}) and for each threshold (Thresh $\in$ [0,1]). Then, the root mean squared error (RMSE) for each of these models is computed and the threshold with the smallest RMSE is selected.

Here, only density-based sparsification and trimming is shown for the clustering coefficient.
```{r, echo=F, message=F, warning=F}
data.bRMSE.full <- data.gvars  %>%
  filter(Variable %in% "cc" ) %>%
  group_by(SparsMethod, ThreshMethod,Thresh) %>%
  mutate("Yhat"=lm(Y~Value, na.action = "na.exclude")$fitted) %>%
  mutate(RMSE=calc_rmse(Y, Yhat),
         R2=calc_rsq(Y,Yhat),
         CS=calc_cs(Y,Yhat)) 

data.bRMSE <- data.bRMSE.full %>%
  dplyr::select(SparsMethod, ThreshMethod, Thresh, RMSE, CS, R2) %>% 
  distinct(Thresh, .keep_all = TRUE)
```


<br>

```{r, echo=F, message=F, warning=F, fig.align='center', fig.width=8, fig.height=5, fig.cap="RMSE  for each of the models using the graph-theoretical features obtained afer sparsification using a certain threshold."}
data.bRMSE %>%
  ggplot(aes(x=Thresh, y=RMSE)) +
  geom_line() +
  theme_bw() +
  facet_grid(SparsMethod~ThreshMethod) +
  geom_vline(data = data.frame(xint=sthresh,SparsMethod="weight-based", ThreshMethod="trim"), aes(xintercept = xint), linetype = "dashed", col="red3")
```

```{r, echo=F, message=F, warning=F}
data.bRMSE.full %>%
  group_by(Subj, SparsMethod, ThreshMethod) %>%
  slice_min(RMSE) %>%
  ggplot(aes(x=Y, y=Yhat))+
  geom_point(shape=1) + 
  geom_abline(intercept = 0, col="red3") +
  theme_bw()+
  facet_grid(SparsMethod~ThreshMethod)
```
```{r}
data.bRMSE %>%
  group_by(SparsMethod, ThreshMethod) %>%
  slice_min(RMSE, with_ties = F) %>%
  mutate_at(4:6, round_0, digits=3) %>%
  kbl(caption="Performance of the best RMSE approach", escape = F) %>%
  row_spec(0, bold=T) %>%
  kable_classic(full_width = T, html_font = "Calibri")%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T, position = "left",fixed_thead = T)
  
```


# Average across sequence
```{r}
# ------ Average feature across threshold sequence
data.AVG.full <- data.gvars %>%
  filter(Variable %in% "cc") %>%
  group_by(SparsMethod, ThreshMethod, Subj, Y) %>%
  summarise("Value.avg"=mean(Value, na.rm=T)) %>%
  group_by(SparsMethod, ThreshMethod) %>%
  mutate("Yhat"=lm(Y~Value.avg, na.action = "na.exclude")$fitted) 

data.AVG <- data.AVG.full %>%
  summarise("RMSE"=calc_rmse(Y,Yhat), "R2"=calc_rsq(Y,Yhat), "CS"=calc_cs(Y,Yhat))
```


```{r, echo=F, message=F, warning=F}
data.AVG.full %>%
  group_by(Subj, SparsMethod, ThreshMethod) %>%
  ggplot(aes(x=Y, y=Yhat))+
  geom_point(shape=1) + 
  geom_abline(intercept = 0, col="red3") +
  theme_bw()+
  facet_grid(SparsMethod~ThreshMethod)
```

<br>

```{r}
data.AVG %>%
  mutate_at(3:5, round_0, digits=3) %>%
  kbl(caption="Performance of the averaging across the sequence approach", escape = F) %>%
  row_spec(0, bold=T) %>%
  kable_classic(full_width = T, html_font = "Calibri")%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T, position = "left",fixed_thead = T)
```

<br>

# References

<div id="refs"></div>
