---
title: 'Auxiliary analysis: General explanations and background of the simulation design'
author: "Mariella Gregorich"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  bookdown::html_document2:
    css: "../src/css_style.css"
    theme: cosmo
    number_sections: true
    keep_md: no
    fig_caption: true
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: 
      collapsed: true
      smooth_scroll: true
    highlight: tango
bibliography: ..\\src\\references.bib 
---



```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = F, warning=F, message=F)

source(here::here("src", "setup.R"))
source(here::here("src", "functions_main.R"))
source(here::here("src", "functions_aux.R"))


scn <- scenarios[190,] 
p = scn$p
n = scn$n
po = (scn$p-1)*scn$p/2 
data_gen_mech = scn$data_gen_mech
data_gen_thresh = scn$data_gen_thresh
data_gen_feature = scn$data_gen_feature
```


# Background

## Network sparsification

In the following we will differentiate between sparsification and thresholding as follows: 
Sparsification will describe the methodology to reduce the network density either by a

- weight-based approach: set edge weights below a fixed cut-off to 0
- density-based approach: set all edge weights not in the top X% to 0 

while thresholding describes the methodology of how retained edge weights are transformed either by

* Weight trimming
\begin{equation}
    \tilde{w}_{rs}=
    \begin{cases}
      w_{rs}, & \text{if}\ w_{rs} > \tau \\
      0, & \text{otherwise}
    \end{cases}
\end{equation}

* Weight binarization
\begin{equation}
    \tilde{w}_{rs}=
    \begin{cases}
      1, & \text{if}\ w_{rs} > \tau \\
      0, & \text{otherwise}
    \end{cases}
\end{equation}

* Weight reshaping
\begin{equation}
    \tilde{w}_{rs}=
    \begin{cases}
      w_{rs}-\tau, & \text{if}\ w_{rs} > \tau \\
      0, & \text{otherwise}
    \end{cases}
\end{equation}


## Graph-theoretical features
The following graph-theoretical features will be examined:
```{r, echo=F, warning=F, message=F}
text_tbl <- data.frame(
  Variable = c("Clustering coefficient", "Characteristic path length", "Modularity", 
            "Assortativity","Diameter", "Eigen-centrality"),
  Explanation = c("The clustering coefficient quantifies the extent of clustering in the network.", 
                  "The characteristic path length is the average paths length of all pairs of nodes.", 
                  "Modularity is a measure of the structure of networks or graphs which measures the strength of division of a network into modules (also called groups, clusters or communities). Networks with high modularity have dense connections between the nodes within modules but sparse connections between nodes in different modules.",
                  "The assortativity coefficient is the Pearson correlation coefficient of degree between pairs of linked nodes. Positive values of r indicate a correlation between nodes of similar degree, while negative values indicate relationships between nodes of different degree.", 
                  "The diameter of a graph is the length of the longest geodesic.", 
                  "The eigenvector centrality is a measure of the influence of a node in a network. Relative scores are assigned to all nodes in the network based on the concept that connections to high-scoring nodes contribute more to the score of the node in question than equal connections to low-scoring nodes.")
)

kbl(text_tbl) %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, width = "30em")
```

## Outcome modelling

Based on the obtained individual-specific networks, graph-theoretical features can be associated with an outcome of interest as follows:

- **OPT**: Thresholding cut-offs between 0 and 1 taken in equidistant steps are sequentially applied to the networks and resulting graph-theoretical features are separately associated with the outcome. The final threshold is the one with the best prediction performance (e.g. RMSPE).
- **AVG**: Thresholding cut-offs between 0 and 1 taken in equidistant steps are sequentially applied to the networks and resulting graph-theoretical features are averaged for each individual and then related to the outcome.
- **FLEX**: Thresholding cut-offs between 0 and 1 taken in equidistant steps are sequentially applied to the networks and the resulting graph-theoretical feature sequence obtained for each individual is related to the outcome through a functional data analysis (FDA) approach.

# Example

In the following chapter, special aspects of the simulation study are considered specifically for one run in order to obtain insights about parameter distributions and the general internal behavior of the approaches.

## Parameter

```{r}
tbl_params <- data.frame("Parameter"=colnames(scn),
                         "Values" =unlist(sapply(scn[1,], as.character)))

tbl_params %>%
  kbl(caption="Parameter of the scnario", escape = F, row.names = F) %>%
  row_spec(0, bold = T) %>%
  kable_classic(full_width = F, html_font = "Calibri")%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T, position = "left",fixed_thead = T)
```

## Simulation design

### Edge weight distribution

```{r, echo=F, warning=F, message=F, fig.align='center', fig.width=6, fig.height=4, fig.cap="Individual-specific variability of edge weights due to the latent processes"}
k=5
df <- generate_data(setting=scn$setting,
                    n = scn$n, 
                    data_gen_feature=scn$data_gen_feature,
                    p = scn$p, 
                    b0 = scn$b0,
                    b1 = scn$b1,  
                    b2 = scn$b2,
                    eps_y = scn$eps_y, 
                    eps_g = scn$eps_g,  
                    data_gen_thresh = scn$data_gen_thresh,
                    data_gen_mech = scn$data_gen_mech)
df$data$fold <- sample(rep(1:5, ceil(n/k)))[1:n]

data.fun <- df$fun
data.graph <- df$data


p1 <- df$data[,c("ID", paste0("GE.", 1:po))] %>%
  pivot_longer(cols=!ID, values_to="Values", names_to="Variable") %>%
  mutate_at(vars(Values), as.numeric) %>%
  ggplot(aes(x=Values, group=ID, col=ID)) +
  geom_density() +
  scale_color_grey() +
  scale_x_continuous("Edge weight", lim=c(0,1)) +
  scale_y_continuous("Density") +
  theme_bw() +
  theme(text=element_text(size=20), legend.position = "None")
p1
ggsave(file = here::here("output", "_figs", "/fig_paper_edgeweight_cc_dist.tiff"),
       width=1.75*100, height=1*100, units="mm", dpi=350, compression = "lzw")
```


```{r, echo=F, warning=F, message=F, fig.align='center', fig.width=6, fig.height=4, fig.cap="Individual-specific variability of edge weights due to the latent processes"}
p2 <- df$data[,c("ID", paste0("GE.noisy.", 1:po))]%>%
  pivot_longer(cols=!ID, values_to="Values", names_to="Variable") %>%
  mutate_at(vars(Values), as.numeric) %>%
  ggplot(aes(x=Values, group=ID, col=ID)) +
  geom_density() +
  scale_x_continuous("Edge weight", lim=c(0,1)) +
  scale_y_continuous("Density") +
  theme_bw() +
  theme(text=element_text(size=20), legend.position = "None")

grid.arrange(p1,p2, nrow=2)
```



### Graph-theoretical features 

```{r, echo=F, warning=F, message=F, fig.align='center', fig.width=12, fig.height=6, fig.caption="Individual-specific variability of graph-theoretical features for XXX individuals"}
true.params <- data.frame("ID"= df$data$ID,
                          "data_gen_thresh"=df$data$data_gen_thresh,
                          "data_gen_mech"=df$data$data_gen_mech,
                          "data_gen_t"=df$data$data_gen_t,
                          "variable"=data_gen_feature)
# Extract network data
po = (p-1)*p/2 
data.network <- df$data[,paste0("GE.noisy.",1:po)]
df$data$fold <- sample(rep(1:5, ceil(n/k)))[1:n]
options(dplyr.summarise.inform = FALSE)

# CC for threshold sequence
data.res <- wrapperThresholding(dat=data.network, set_ids=unique(df$data$ID), mdim=p, 
                                step_size = step_size, graph_feature=data_gen_feature)

# Add outcome Y
data.gvars <- merge(df$data[,c("ID","Y", "X", "fold")], data.res, by="ID") %>%
  mutate(value=ifelse(is.nan(value), NA, value)) %>%
  mutate_at(vars(data_ana_t, Y, value), as.numeric) %>%
  filter(variable %in% data_gen_feature) %>%
  dplyr::rename("value.noisy"=value)

# Add noisy value
data.gvars <- merge(df$abide, data.gvars, by=c("ID", "data_ana_thresh", "data_ana_t", "variable")) %>%
  relocate(value, .before = value.noisy)
```


```{r, echo=F, warning=F, message=F, fig.align='center', fig.width=6, fig.height=4, fig.caption="Individual-specific variability of graph-theoretical features for XXX individuals"}
subset_ids <- unique(data.gvars$ID)[sample(1:length(unique(data.gvars$ID)),10)]
df.tmp <- data.gvars %>% 
  melt(id.vars = colnames(data.gvars)[1:7], value.name = "values") 
colnames(df.tmp)[4] <- "feature"

df.tmp %>%
  filter(data_ana_thresh %in% "weight-based") %>%
  ggplot(aes(x=data_ana_t, y=values, group=paste0(ID, "_", variable), col=ID)) +
  geom_line() +
  scale_x_continuous("Threshold") +
  scale_y_continuous("Characteristic path length") +
  theme_bw() +
  scale_color_grey() +
  #facet_grid(feature~data_ana_thresh) +
  theme(plot.title = element_text(hjust = 0.5), 
        text = element_text(size=16),
        legend.position = "None")
ggsave(file = here::here("output", "_figs", "/fig_paper_gfea_wb_cpl_dist.tiff"),
       width=1.75*100, height=1.25*100, units="mm", dpi=350, compression = "lzw")
```
<br>

```{r}
cc <- data.gvars %>% filter(data_ana_t==0.25 & data_ana_thresh=="weight-based") %>% pull(value)
cc_noisy <- data.gvars %>% filter(data_ana_t==0.25 & data_ana_thresh=="weight-based") %>% pull(value.noisy)
plot(cc, cc_noisy, xlim = c(0.2,1), ylim=c(0.2,1))
abline(coef = c(0,1))
cor(cc, cc_noisy)
```


### Outcome

```{r, fig.align='center', fig.width=6, fig.height=4, fig.cap="Distribution of the outcome variable"}
data.gvars %>%
  dplyr::select(ID, Y) %>%
  distinct(Y, keep.all=T) %>%
  ggplot(aes(x=Y))+
  geom_histogram(col="black", fill="gray80") +
  ggtitle("Histogram of the outcome Y") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5), text = element_text(size=14))
```
<br>


### Functional form of sequence

In the following selection, the three functional forms for data generation using the sequence of graph-theoretical features are first illustrated. In the following, the average RMSPE function for each threshold value t is first calculated in an unstandardized and then in a standardized way. The calculation is performed for each threshold t by taking the root of the mean squared difference between the true beta(t) value at t and the estimated over all iterations.

```{r, echo=F, warning=F, message=F}
b1 <- as.numeric(scn$b1[1])
thr.steps = seq(0,1,0.0005)
true.opt = ifelse(thr.steps==0.25, scn$b1, NA)
true.flat = rep(4,length(thr.steps))
true.halfsine = ifelse(thr.steps >0.5, 0, sin(thr.steps*pi*2)*6.5)
true.sine = sin(thr.steps*pi)*6
true_fun <- data.frame("thresh"= thr.steps,
                       "flat"= true.flat,
                       "half-sine"=true.halfsine,
                       "sine"=true.sine)

thr.weight <- round(runif(scn$n, min=0.1, max=0.4),3)
true.random <- data.frame("ID"=data.graph$ID, "thresh"=thr.weight, "value"=scn$b1, "variable"="random")

true_fun_melted <- melt(true_fun, id.vars = "thresh") %>%
  mutate(variable=fct_recode(variable, "half-sine"="half.sine")) 
```


```{r, echo=F, warning=F, message=F, fig.align='center', fig.width=8, fig.height=3, fig.cap="The three true functional forms used in the data-generating mechanism to generated the outcome based on a graph-theoretical feature sequence derived by sequential weight-based sparsification"}
true.opt <- data.frame("ID"=scn$n, "thresh"=thr.steps, "value"=ifelse(thr.steps==0.25, scn$b1, NA), "variable"="single")

true.hs <- data.frame("ID"=scn$n, "thresh"=thr.steps, "value"=true.halfsine, "variable"="half-sine")

true.scn <- data.frame(rbind(true.opt, true.random, true.hs)) %>%
  mutate(variable=fct_relevel(variable, c("single", "random", "half-sine"))) %>%
  rename(variable=variable)


# Labeller ggplot
funform_names <- list(
  'single'="Universal threshold",
  'random'="Individual-specific threshold",
  'flat'="Flat form",
  'half-sine'="Half-sine form",
  'sine'="Sine form"
)
funform_labeller <- function(variable,value){
  return(funform_names[value])
}


p1 <- true.scn %>%
  filter(variable %in% "single") %>%
  ggplot(aes(x=thresh, y=value, group=ID)) +
  geom_vline(xintercept = 0.25, linetype=2, col="grey") +
  geom_point(col="blue") +
  geom_line(data=data.frame(ID=c(rep(1, length(seq(0,0.24,0.01))), rep(2, length(seq(0.26,1,0.01)))),
                            thresh=c(seq(0,0.24,0.01),seq(0.26,1,0.01)),value=0), col="blue") +
  theme_bw() +
  facet_grid(~variable, labeller = funform_labeller)+
  scale_x_continuous("", limits=c(0,1)) +
  scale_y_continuous("Coefficient \u03b2", limits=c(-30,30)) +
  theme(legend.position = "None",
        text=element_text(size=14))
p2 <- true.scn %>%
  dplyr::filter(variable %in% "random" & ID %in% sample(unique(data.gvars$ID),5)) %>%
  ggplot(aes(x=thresh, y=value, col=ID)) +
  geom_point(size=4) +
  theme_bw() +
  geom_vline(xintercept = c(0.1, 0.4), linetype=2, col="grey") +
  facet_grid(~variable, labeller = funform_labeller)+
  geom_label(data = data.frame(ID=unique(data.gvars$ID)[1], thresh=0.5, value=-10),label = expression(t[opt,i]*" for n=5!"), size=5) +
  scale_x_continuous("", limits=c(0,1)) +
  scale_y_continuous("", limits=c(-30,30)) +
  theme(legend.position = "None",
        text=element_text(size=14))
p <- grid.arrange(p1,p2, nrow=1, bottom = ggpubr::text_grob("Threshold", vjust=-1))
p
ggsave(file = here::here("output", "_figs", "/fig_threshold_true.tiff"),plot = p,
       width=2*100, height=0.75*100, units="mm", dpi=350, compression = "lzw")
```

<br>

```{r, echo=F, warning=F, message=F, fig.align='center', fig.width=8, fig.height=3, fig.cap="The three true functional forms used in the data-generating mechanism to generated the outcome based on a graph-theoretical feature sequence derived by sequential weight-based sparsification"}
true_fun_melted %>%
ggplot(aes(x=thresh, y=value)) +
  geom_line(col="blue") +
 # ggtitle("True functional form of data generation") +
  facet_grid(~ variable, labeller = funform_labeller) +
  theme_bw() +
  scale_x_continuous("Threshold") +
  scale_y_continuous(paste0("Coeficient function \u03b2(t)")) +
  theme(text = element_text(size=12))
ggsave(file = here::here("output", "_figs", "/fig_funform_true.tiff"),
       width=2*100, height=0.75*100, units="mm", dpi=350, compression = "lzw")
```



<br>

## Methods

```{r}
data.gvars <- data.gvars %>%
  dplyr::select(!value) %>%
  rename(value=value.noisy)
```


```{r}

# --  Oracle model
# Data preparation for oracle model
if(data_gen_mech %in% c("single","random")){
  data.oracle <- data.gvars %>%
    filter(data_ana_thresh == true.params$data_gen_thresh &
             variable == true.params$variable) %>%
    group_by(data_ana_t) %>%
    mutate("true.t"=df$data$data_gen_t) %>%
    filter(data_ana_t == round(true.t,2)) %>%
    dplyr::select(!true.t) 
}else if(data_gen_mech %in% c("half-sine", "sine")){
  mat.gvars <- data.gvars %>%
    filter(data_ana_thresh == true.params$data_gen_thresh &
             variable == true.params$variable) %>%
    dplyr::select(ID, data_ana_t, value) %>%
    arrange(data_ana_t) %>%
    pivot_wider(names_from = "data_ana_t", values_from = "value") %>%
    dplyr::select(!ID)
  prod.beta.Xg <- t(t(mat.gvars) * df$fun$betafun_true)*step_size
  Xg <- rowSums(prod.beta.Xg)
  
  data.oracle <- data.gvars %>%
    filter(data_ana_thresh == true.params$data_gen_thresh &
             variable == true.params$variable & data_ana_t == 0) %>%
    mutate(value = Xg)
}

unused_data_gen_thresh <- ifelse(data_gen_thresh %in% "density-based", "weight-based", "density-based")
data.oracle <- data.oracle %>%
  group_by(data_ana_thresh, variable) %>%
  nest() %>%
  mutate(res.oracle=lapply(data, function(x) perform_AVG(dat=x, k=k, adjust=F, family = "gaussian"))) %>%
  unnest(res.oracle) %>%
  mutate("data_ana_model"="Oracle") %>%
  bind_rows(. , expand.grid("data_ana_model"="Oracle", "adjust"=FALSE, "data_ana_thresh"=unused_data_gen_thresh, 
                            "data_ana_t"=NA, "variable"=data_gen_feature,"RMSPE"=NA, "R2"=NA, "CS"=NA))
  
  

# --  Null model
data.null <- df$data %>%
  dplyr::select(ID, fold, Y, X) %>%
  mutate(data_ana_thresh = data_gen_thresh,
         variable = data_gen_feature,
         value = mean(Y)) %>%
  group_by(data_ana_thresh, variable) %>%
  nest() %>%
  mutate(res=lapply(data, function(x) rbind(perform_AVG(dat=x, k=k, adjust=F, family = "gaussian"),
                                            perform_AVG(dat=x, k=k, adjust=T, family = "gaussian")))) %>%
  unnest(res) %>%
  mutate("data_ana_model"="Null",
         data_ana_t=as.character(data_ana_t)) %>% 
  slice(rep(1:n(), times = 2)) %>%
  mutate(data_ana_thresh = rep(c("weight-based", "density-based"), each=2))
  


# -- Pick model with best RMSPE
threshold_OPT <- data.frame(data_ana_thresh = c("weight-based", "density-based"), threshold_lo =c(0, .25), threshold_up =c(.75, 1))
data.OPT <- data.gvars  %>% 
  left_join(threshold_OPT, by = 'data_ana_thresh') %>%
  filter(data_ana_t >= threshold_lo & data_ana_t <= threshold_up) %>%
  group_by(data_ana_thresh, variable) %>%
  nest() %>%
  mutate(res=lapply(data, function(x) rbind(perform_OPT(dat=x, k=k, adjust=F, family = "gaussian"), 
                                            perform_OPT(dat=x, k=k, adjust=T, family = "gaussian")))) %>%
  unnest(res, keep_empty = T) %>%
  mutate("data_ana_model"="OPT",
         "data_ana_t"=as.character(data_ana_t)) 


# --  Average feature across threshold sequence
threshold_AVG <- data.frame(data_ana_thresh = c("weight-based", "density-based"),  threshold_lo =c(.1, .6), threshold_up =c(.4, .9))
data.AVG <- data.gvars %>%
  left_join(threshold_AVG, by = 'data_ana_thresh') %>%
  filter(data_ana_t >= threshold_lo & data_ana_t <= threshold_up) %>%
  group_by(data_ana_thresh, variable, ID, Y, X, fold) %>%
  summarise("value.avg"=mean(value, na.rm=T)) %>%
  dplyr::rename(value=value.avg) %>%
  group_by(data_ana_thresh, variable) %>%
  nest() %>%
  mutate(res=lapply(data, function(x) rbind(perform_AVG(dat=x, k=k, adjust=F, family = "gaussian"), 
                                            perform_AVG(dat=x, k=k, adjust=T, family = "gaussian")))) %>%
  unnest(res, keep_empty = T) %>%
  mutate("data_ana_model"="AVG",
         data_ana_t=as.character(data_ana_t)) 


# --  Functional data analysis approach
data.FLEX <- data.gvars %>%
  arrange(data_ana_t) %>%
  mutate(data_ana_t=paste0("T_",data_ana_t),
         Y = as.numeric(as.character(Y)),
         SM=data_ana_thresh) %>%
  pivot_wider(values_from = value, names_from = data_ana_t) %>%
  group_by(data_ana_thresh, variable) %>%
  nest() %>%
  mutate(res=lapply(data, function(x) rbind(perform_FLEX(data.fda=x, k=k, adjust=F, family = "gaussian"),
                                            perform_FLEX(data.fda=x, k=k, adjust=T, family = "gaussian")))) %>%
  unnest(res) %>%
  mutate("data_ana_model"="FLEX",
         data_ana_t=as.character(data_ana_t))
```



## Results

Results of one iteration with a true R2 of `r round_0(data.graph$true.R2[1],2)` and a true threshold cut-off of `r data.graph$true.threshold[1] `

### Functional form $\beta(t)$

#### Penalized splines

```{r, fig.align='center', fig.width=8, fig.height=5, fig.cap="Coefficient function of the FLEX approach with penalized splines and 20 nodes"}
data.FLEX.coeff <- data.FLEX %>%
  dplyr::select(variable, data_ana_model, adjust, data_ana_thresh, coef) %>%
  unnest(coef) %>%
  reduce(data.frame) %>%
  `colnames<-`(c("variable", "data_ana_model", "adjust","data_ana_thresh", 
                 "fda.thresh", "fda.est", "fda.se", "fda.sd.Xt")) %>%
  merge(., data.fun, by.x="fda.thresh", by.y="grid")
```

```{r, fig.align='center', fig.width=8, fig.height=6, fig.cap="Unstandardized coefficient function modelled for the clustering coefficient by penalized splines with 20 nodes"}
data.FLEX.coeff %>%
  filter(variable %in% scn$data_gen_feature) %>%
  mutate(fda.est.lo=fda.est - 1.96 * fda.se,
         fda.est.up=fda.est + 1.96 * fda.se) %>%
  ggplot(aes(x=fda.thresh, y=fda.est, ymin=fda.est.lo, ymax=fda.est.up, col=data_ana_thresh)) +
  geom_line() +
  geom_ribbon(alpha=0.1) +
  scale_y_continuous("Coefficient function") +
  scale_x_continuous("Threshold") +
  facet_grid(data_ana_thresh~adjust, scales = "free_y") +
  theme_bw() 
```

<br>

```{r, fig.align='center', fig.width=8, fig.height=6, fig.cap="Standardized coefficient function modelled for the clustering coefficient by penalized splines with 20 nodes"}
data.FLEX.coeff %>%
  filter(variable %in% scn$data_gen_feature) %>%
  mutate(fda.est.std = fda.est * fda.sd.Xt,
         fda.est.lo=fda.est - 1.96 * fda.se,
         fda.est.up=fda.est + 1.96 * fda.se,
         fda.est.std.lo=fda.est.lo * fda.sd.Xt,
         fda.est.std.up=fda.est.up * fda.sd.Xt) %>%
  ggplot(aes(x=fda.thresh, y=fda.est.std, ymin=fda.est.std.lo, ymax=fda.est.std.up, col=data_ana_thresh)) +
  geom_line() +
  geom_ribbon(alpha=0.1) +
  scale_y_continuous("Coefficient function") +
  scale_x_continuous("Threshold") +
  theme_bw() +
  facet_grid(data_ana_thresh~adjust, scales = "free_y")
```

<!-- <br> -->

<!-- ```{r, fig.align='center', fig.width=8, fig.height=5, fig.cap="Product of coefficient function and functional covariate of the FLEX approach with penalized splines and 20 nodes"} -->
<!-- mat.gvars <- data.gvars %>% -->
<!--   arrange(Thresh)%>% -->
<!--   dplyr::select(!Value) %>% -->
<!--   mutate(Thresh=paste0("T_",Thresh)) %>% -->
<!--   pivot_wider(values_from = Value, names_from = Thresh) %>% -->
<!--   group_by(data_ana_thresh, ThreshMethod, Variable) %>% -->
<!--   nest()  -->
<!-- mat.gvars <- as.data.frame(mat.gvars[1,]$data) -->
<!-- mat.gvars <- apply(mat.gvars[,4:54],2, as.numeric) -->
<!-- betat.hat <- as.numeric(data.FLEX.coeff[data.FLEX.coeff$data_ana_thresh == "weight-based",]$fda.est) -->

<!-- prod.betaX.hat <- t(betat.hat * t(mat.gvars)) -->

<!-- prod.betaX.hat <- prod.betaX.hat %>% -->
<!--   melt() %>% -->
<!--   mutate("grid"= as.numeric(str_remove(Var2, "T_"))) %>% -->
<!--   dplyr::select(Var1, value, grid) %>% -->
<!--   `colnames<-`(c("ID", "value", "grid")) %>% -->
<!--   mutate("group"="estimate") -->

<!-- prod.betaX.true <- t(data.fun$betafn.true * t(mat.gvars)) *scn$b1/5 -->

<!-- prod.betaX.true <- data.frame("ID"=1:n, prod.betaX.true) %>% -->
<!--   melt(id.vars="ID") %>% -->
<!--   mutate("grid"=as.numeric(str_remove(as.character(variable), "T_"))) %>% -->
<!--   dplyr::select(ID, value, grid) %>% -->
<!--   `colnames<-`(c("ID", "value", "grid")) %>% -->
<!--   mutate("group"="true") -->


<!-- prod.betaX <- data.frame(rbind(prod.betaX.hat, prod.betaX.true)) -->

<!-- p <- ggplot(data=prod.betaX, aes(x=grid, y=value, group=ID, col=ID)) + -->
<!--    geom_line() + -->
<!--    facet_grid(~group) + -->
<!--    theme_bw() + -->
<!--   theme(text=element_text(size=16)) -->

<!-- if(all(is.na(prod.betaX.true$value))){ -->
<!--   p <- p + geom_label(data = data.frame(ID=1, grid=0.5, value=mean(prod.betaX$value, na.rm=T), group="true"), -->
<!--                                      label = "No true functional form selected!", size=5) -->
<!-- }  -->
<!-- p -->
<!-- ``` -->

<br>


### Overall

```{r}
data.results <- data.frame(rbind(
    data.null[,c("data_ana_model", "adjust", "data_ana_thresh", "data_ana_t","variable","RMSPE", "R2", "CS")],
    data.oracle[,c("data_ana_model","adjust", "data_ana_thresh", "data_ana_t","variable","RMSPE", "R2", "CS")],
    data.OPT[,c("data_ana_model","adjust", "data_ana_thresh", "data_ana_t","variable","RMSPE", "R2", "CS")],
    data.AVG[,c("data_ana_model","adjust", "data_ana_thresh", "data_ana_t","variable","RMSPE", "R2", "CS")],
    data.FLEX[,c("data_ana_model","adjust", "data_ana_thresh", "data_ana_t","variable","RMSPE", "R2", "CS")])) %>%
  group_by(data_ana_thresh) %>%
  filter(adjust==FALSE) %>%
  mutate(relRMSPE = RMSPE/min(RMSPE, na.rm=T))
```


```{r}
data.results %>%
  filter(data_ana_thresh %in% "weight-based") %>%
  mutate_at(6:9, as.numeric) %>%
    mutate_at(6:9, round_0, 3) %>%
  arrange(RMSPE) %>%
  kbl(caption="Results of one iteration", 
      escape = F, row.names = F) %>%
  row_spec(0, bold = T) %>%
  column_spec(c(2:5), extra_css="text-align: center") %>%
  kable_classic(full_width = F, html_font = "Calibri")%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T, position = "left",fixed_thead = T)
```

<br>

```{r}
data.results %>%
  filter(data_ana_thresh %in% "density-based") %>%
  mutate_at(6:9, as.numeric) %>%
    mutate_at(6:9, round_0, 3) %>%
  arrange(RMSPE) %>%
  kbl(caption="Results of one iteration", 
      escape = F, row.names = F) %>%
  row_spec(0, bold = T) %>%
  column_spec(c(2:5), extra_css="text-align: center") %>%
  kable_classic(full_width = F, html_font = "Calibri")%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T, position = "left",fixed_thead = T)
```


# References

<div id="refs"></div>