---
title: 'Auxiliary analysis: Data generation by beta transform'
author: "Mariella Gregorich"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  bookdown::html_document2:
    css: "../src/css_style.css"
    theme: cosmo
    number_sections: true
    keep_md: no
    fig_caption: true
    code_folding: show
    toc: true
    toc_depth: 2
    toc_float: 
      collapsed: true
      smooth_scroll: true
    highlight: tango
bibliography: ..\\src\\references.bib 
---



```{r setup, include=F}
rm(list=ls())
knitr::opts_chunk$set(echo = F, warning=F, message=F)
pacman::p_load(ggplot2, tidyr, dplyr)
set.seed(666)
```

# Background

Let us define 
\begin{equation}
\tag{1}
\eta_i(r,s) := \alpha_0(r,s) + \alpha_1(r,s)X_{1i} + \alpha_2(r,s)X_{2i}, 
\end{equation}
with
\begin{equation}
\alpha_0 \sim N(0,1) \\
\alpha_1, \alpha_2 \sim U(0,1) \\
X_1, X_2 \sim N(0,1)
\end{equation}

We want 
\begin{equation}
f: R:=\{\eta_i(r,s):(r,s) \in E\} \rightarrow (0,1) \\
or \\
f(\eta_i) \sim \beta(a,b)
\end{equation}


For this we simulate $\alpha_0, \alpha_1, \alpha_2, X_1 and X_2$ from their corresponding distribution, compute the z-score $\eta_i(r,s)$ and then obtain its probability $p$ via the distribution function pnorm() at $\eta_i(r,s)$. 

In order to do so, we have to derive the mean and variance of $\eta \sim N(\mu, \sigma)$ via
\begin{equation}
E(\eta)=E(\alpha_0+\alpha_1 X_1+\alpha_2 X_2) \\
Var(\eta)=Var(\alpha_0+\alpha_1 X_1+\alpha_2 X_2)
\end{equation}
Lastly, we use the $\beta$-quantile function (inverse cumulative distribution function) with the prespecified shape parameters to determine the value corresponding to the $p$th-quantile of our beta distribution.



# Define shape of beta distribution
```{r, echo=T}
n=250 # number of individuals
p=50 # number of nodes
po=(p*(p-1))/2 # number of potential edges
distr.params=list("beta"=c("shape1"=4, "shape2"=2), 
                  "alpha12.unif"=c("min"=0, "max"=3), 
                  "alpha0.norm"=c("mean"=2, "sd"=0.5), 
                  "X.norm"=c("mean"=0, "sd"=1)) 

```


```{r, echo=F, fig.align='center', fig.cap="The beta distribution the edge weights should follow"}
df <- data.frame("Subj"=0, "Weight"=rbeta(po, distr.params$beta[1], distr.params$beta[2]))

ggplot(df, aes(x = Weight, colour = Subj, group=Subj)) +
  geom_histogram(col="black", fill="lightgrey") +
  theme_bw() +
  theme(legend.position = "None")
```

<br>

# Transform normal distribution to beta distribution


## Procedure
```{r, echo=T}

calc_eta_mean_and_var <- function(alpha0.norm.pars, alpha12.unif.pars, X.norm.pars){
  # alpha0~N(mean1,std1), alpha1~U(a,b), alpha2~U(a.b)
  # X1~N(mean2,sd2), X2~N(mean2,sd2)
  alpha12.unif.mean = (alpha12.unif.pars["max"]-alpha12.unif.pars["min"])/2
  alpha12.unif.var = ((1/12)*(alpha12.unif.pars["max"]-alpha12.unif.pars["min"])^2)
  
  V=alpha0.norm.pars["sd"]^2 + 2*(((alpha12.unif.var +alpha12.unif.mean^2)*(X.norm.pars["sd"]^2+X.norm.pars["mean"]^2))-
                                    (alpha12.unif.mean^2*X.norm.pars["mean"]^2))
  S=sqrt(V)
  M=alpha0.norm.pars["mean"] + alpha12.unif.mean * X.norm.pars["mean"] + alpha12.unif.mean * X.norm.pars["mean"]
  return(list("mean"=as.numeric(M), "sd"=as.numeric(S)))
}

gen_quantiles <- function(alpha0, alpha1, alpha2, X1, X2, beta.pars, eta.pars){
  # X1=X1[1]; X2=X2[1];beta.pars = distr.params$beta; eta.pars = eta.params
  
  eta = alpha0 + alpha1 * X1 + alpha2 * X2
  p = pnorm(eta, mean=eta.pars$mean, sd=eta.pars$sd)
  q = qbeta(p, beta.pars[1], beta.pars[2])
  return(data.frame("eta"=eta, "p"=p, "q"=q))
}


alpha0 = rnorm(po, distr.params$alpha0.norm[1], distr.params$alpha0.norm[2])
alpha1 = runif(po, distr.params$alpha12.unif[1], distr.params$alpha12.unif[2])
alpha2 = runif(po, distr.params$alpha12.unif[1], distr.params$alpha12.unif[2])

X1=rnorm(n,0,1)
X2=rnorm(n,0,1)

eta.params <- calc_eta_mean_and_var(alpha0.norm.pars=distr.params$alpha0.norm, 
                                    X.norm.pars=distr.params$X.norm,
                                    alpha12.unif.pars=distr.params$alpha12.unif)
vec <-lapply(1:n, function(x) data.frame("Subj"=x, gen_quantiles(alpha0, alpha1, alpha2, X1[x], X2[x], 
                                                                 beta.pars = distr.params$beta, eta.pars = eta.params)))
df <- data.frame(do.call(rbind, vec))
```


```{r, fig.align='center', fig.cap="Density plot of edge weights by subject"}
ggplot(df, aes(x = q, colour = Subj, group=Subj)) +
  geom_density() +
  scale_x_continuous("Edge weights") +
  theme_bw() +
  theme(legend.position = "None")
```

<br>

## Examples


```{r, fig.align='center', fig.cap="Random individual-specific edge weight distributions"}
ggplot(df[df$Subj%in%1:15,], aes(x = q, colour = Subj, group=Subj)) +
  geom_histogram(col="black", fill="lightgrey") +
  theme_bw() +
  theme(legend.position = "None") +
  facet_wrap(~Subj, nrow=3)
```



<br>



# Issues (last updated 25/03/2022)

(1) Both approaches for simulating individual-specific networks do not deliver the desired variability around a mean network and its edge weight distribution. Namely that the edge weight distribution $\alpha_0 \sim \beta(1.15,0.75)$ and that the latent processes $X_1$ and $X_2$ vary proportionally to the predefined edge effect weights $\alpha_1$ and $\alpha_2$ around the respective $\alpha_0(r,s)$.

(2) Derivation of the mean and variance of $\eta$ if $X=[X_1, X_2] \sim MN(M, \Sigma)$ ?