---
title: 'Auxiliary analysis: Error estimation for noise(Y) and noise(G)'
author: "Mariella Gregorich"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  bookdown::html_document2:
    css: "../src/css_style.css"
    theme: cosmo
    number_sections: true
    keep_md: no
    fig_caption: true
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: 
      collapsed: true
      smooth_scroll: true
    highlight: tango
bibliography: ..\\src\\references.bib 
---

```{r setup, include=FALSE}
rm(list=ls())
#knitr::opts_chunk$set(echo = F, warning=F, message=F)
set.seed(666)

source(here::here("src", "setup.R"))
source(here::here("src", "functions_main.R"))
source(here::here("src", "functions_aux.R"))

N = 75
P = 150
rps = 3
```



```{r}
compute_scnR2 <- function(scn){
  # scn = data.frame(scenarios.single[7,])
  sourceCpp(here::here("src","utils.cpp"))
  scn <- data.frame(scn)
  p = scn$p
  n = scn$n
  po = (scn$p-1)*scn$p/2  
  k=5
  

  R2 <- rep(NA, rps)
  for(i in 1:rps){

  # Data generation
  data.gen <- generate_data(setting = scn$setting,
                               n = scn$n, 
                               data_gen_feature = scn$data_gen_feature,
                               p = scn$p, 
                               b0 = scn$b0,
                               b1 = scn$b1,  
                               b2 = scn$b2,
                               eps_y = scn$eps_y, 
                               eps_g = scn$eps_g, 
                               data_gen_thresh = scn$data_gen_thresh,
                               data_gen_mech = scn$data_gen_mech)
  data.fun <- data.gen$fun
  data.graph <- data.gen$data
  
  if(scn$eps_g == 0){
    R2[i] <- cor(data.graph$Y, data.graph$Xg)^2
  }else{
    # Estimation of the graph-theoretical features
    data.network <- data.gen$data[,paste0("GE.noisy.",1:po)]
    data.gen$data$fold <- sample(rep(1:5, ceil(n/k)))[1:n]
    options(dplyr.summarise.inform = FALSE)
    data_gen_feature <- as.character(scn$data_gen_feature)
    
    # CC for threshold sequence
    data.res <- wrapperThresholding(dat=data.network, set_ids=unique(data.gen$data$ID), mdim=p, 
                                  step_size = step_size, graph_feature=data_gen_feature)
    
    # Add outcome Y
    data.gvars <- merge(data.gen$data[,c("ID","Y", "X", "fold")], data.res, by="ID") %>%
      mutate(value=ifelse(is.nan(value), NA, value)) %>%
      mutate_at(vars(data_ana_t, Y, value), as.numeric) %>%
      filter(variable %in% data_gen_feature) 
  
    
    # Estimation of the oracle model
    true.params <- data.frame("ID"= data.gen$data$ID,
                              "data_gen_thresh"=data.gen$data$data_gen_thresh,
                              "data_gen_mech"=data.gen$data$data_gen_mech,
                              "data_gen_t"=data.gen$data$data_gen_t,
                              "variable"=data_gen_feature)
          
    # --  Oracle model
    # Data preparation for oracle model
    if(scn$data_gen_mech %in% c("single","random")){
      data.oracle <- data.gvars %>%
        filter(data_ana_thresh == true.params$data_gen_thresh &
                 variable == true.params$variable) %>%
        group_by(data_ana_t) %>%
        mutate("true.t"=data.gen$data$data_gen_t) %>%
        filter(data_ana_t == round(true.t,2)) %>%
        dplyr::select(!true.t) 
    }else if(scn$data_gen_mech %in% c("flat", "half-sine", "sine")){
      mat.gvars <- data.gvars %>%
        filter(data_ana_thresh == true.params$data_gen_thresh &
                 variable == true.params$variable) %>%
        dplyr::select(ID, data_ana_t, value) %>%
        arrange(data_ana_t) %>%
        pivot_wider(names_from = "data_ana_t", values_from = "value") %>%
        dplyr::select(!ID)
      prod.beta.Xg <- t(t(mat.gvars) * data.gen$fun$betafun_true)*step_size
      Xg <- rowSums(prod.beta.Xg)
      
      data.oracle <- data.gvars %>%
        filter(data_ana_thresh == true.params$data_gen_thresh &
                 variable == true.params$variable & data_ana_t == 0) %>%
        mutate(value = Xg)
    }
    
    data.oracle <- data.oracle %>%
      group_by(data_ana_thresh, variable) %>%
      nest() %>%
      mutate(res.oracle=lapply(data, function(x) perform_AVG(dat=x, k=k, adjust=F, family = "gaussian"))) %>%
      unnest(res.oracle) %>%
      mutate("data_ana_model"="Oracle")
      
      R2[i] <- data.oracle$R2
    }    
  }

  
  return(mean(R2))
}
```

# Setting: uni

* Sample size n = `r N`
* Nodes p = `r P`
* Results averaged over 10 runs
* Previous value of Noise(Y)=[0, 0.5, 1]
* Previous values of Noise(G)=[0, 0.05, 0.1] (but now Noise(G) added to $\eta_i$, so not comparable)


## Scenario: single threshold = 0.25

```{r single_u}
# --- Scenario: single threshold = 0.25
scenarios$R2 <- NA
scenarios.single <- scenarios %>% filter(n==N & data_gen_mech == "single" & data_gen_thresh == "weight-based" & data_gen_feature == "cpl")
plan(multisession, workers=detectCores()*.75)
scenarios.single$R2 <- future_sapply(1:nrow(scenarios.single), function(x) compute_scnR2(data.frame(scenarios.single[x,])), future.seed=TRUE)
scenarios.single$R2 <- round(scenarios.single$R2,2)
plan(sequential)
xtabs(R2~eps_y+eps_g, data = scenarios.single)
```


## Scenario: random threshold U(0.1,0.4)
```{r random_u}
# --- Scenario: random threshold U(0.1,0.4)
scenarios.random <-  scenarios %>% filter(n==N & data_gen_mech == "random" & data_gen_thresh == "weight-based" & data_gen_feature == "cpl")
plan(multisession, workers=detectCores()*.75)
scenarios.random$R2 <- future_sapply(1:nrow(scenarios.random), function(x) compute_scnR2(data.frame(scenarios.random[x,])), future.seed=TRUE)
scenarios.random$R2 <- round(scenarios.random$R2,2)
plan(sequential)
xtabs(R2~eps_y+eps_g, data = scenarios.random)

```

## Scenario: functional form = flat
```{r flat_u}
# --- Scenario: functional form
scenarios.func1 <-  scenarios %>% filter(n==N & data_gen_mech == "flat" & data_gen_thresh == "weight-based" & data_gen_feature == "cpl")
plan(multisession, workers=detectCores()*.75)
scenarios.func1$R2 <- future_sapply(1:nrow(scenarios.func1), function(x) compute_scnR2(data.frame(scenarios.func1[x,])), future.seed=TRUE)
scenarios.func1$R2 <- round(scenarios.func1$R2,2)
plan(sequential)
xtabs(R2~eps_y+eps_g, data = scenarios.func1)
```

## Scenario: functional form = half-sine

```{r halfsine_u}
# --- Scenario: functional form
scenarios.func2 <- scenarios %>% filter(n==N & data_gen_mech == "half-sine" & data_gen_thresh == "weight-based" & data_gen_feature == "cpl")
plan(multisession, workers=detectCores()*.75)
scenarios.func2$R2 <- future_sapply(1:nrow(scenarios.func2), function(x) compute_scnR2(data.frame(scenarios.func2[x,])), future.seed=TRUE)
scenarios.func2$R2 <- round(scenarios.func2$R2,2)
plan(sequential)
xtabs(R2~eps_y+eps_g, data = scenarios.func2)
```


## Scenario: functional form = sine

```{r sine_u}
# --- Scenario: functional form
scenarios.func3 <- scenarios %>% filter(n==N & data_gen_mech == "half-sine" & data_gen_thresh == "weight-based" & data_gen_feature == "cpl")
plan(multisession, workers=detectCores()*.75)
scenarios.func3$R2 <- future_sapply(1:nrow(scenarios.func3), function(x) compute_scnR2(data.frame(scenarios.func3[x,])), future.seed=TRUE)
scenarios.func3$R2 <- round(scenarios.func3$R2,2)
plan(sequential)
xtabs(R2~eps_y+eps_g, data = scenarios.func3)
```


# Setting: latent

* Sample size n = `r N`
* Nodes p = `r P`
* Results averaged over 10 runs


## Scenario: single threshold = 0.25
```{r single_l}
# --- Scenario: single threshold = 0.25
scenarios$R2 <- NA
scenarios.single <- scenarios %>% filter(n==N & names(dg.thresh) == "single"  & setting == "latent")

plan(multisession, workers=detectCores()*.75)
scenarios.single$R2 <- future_sapply(1:nrow(scenarios.single), function(x) compute_scnR2(scenarios.single[x,]), future.seed=TRUE)
scenarios.single$R2 <- round(scenarios.single$R2,2)
plan(sequential)
xtabs(R2~eps.y+eps.g, data = scenarios.single)
```


## Scenario: random threshold U(0.1,0.4)
```{r random_l}
# --- Scenario: random threshold U(0.1,0.4)
scenarios$R2 <- NA
scenarios.random <- scenarios %>% filter(n==N & p==P & names(dg.thresh) == "random"  & setting == "latent" & outcome=="prognostic")

plan(multisession, workers=detectCores()*.75)
scenarios.random$R2 <- future_sapply(1:nrow(scenarios.random), function(x) compute_scnR2(data.frame(scenarios.random[x,])), future.seed=TRUE)
scenarios.random$R2 <- round(scenarios.random$R2,2)
plan(sequential)
xtabs(R2~eps.y+eps.g, data = scenarios.random)
```


## Scenario: functional form = flat
```{r flat_l}
# --- Scenario: functional form
scenarios.func1 <- scenarios %>% filter(n==N & p==P & dg.thresh == "flat" & setting == "latent" & outcome=="prognostic")
plan(multisession, workers=detectCores()*.75)
scenarios.func1$R2 <- future_sapply(1:nrow(scenarios.func1), function(x) compute_scnR2(data.frame(scenarios.func1[x,])), future.seed=TRUE)
scenarios.func1$R2 <- round(scenarios.func1$R2,2)
plan(sequential)
xtabs(R2~eps.y+eps.g, data = scenarios.func1)
```

## Scenario: functional form = half-sine

```{r halfsine_l}
# --- Scenario: functional form
scenarios.func2 <- scenarios %>% filter(n==N & p==P & dg.thresh == "half-sine" & setting == "latent" & outcome=="prognostic")
plan(multisession, workers=detectCores()*.75)
scenarios.func2$R2 <- future_sapply(1:nrow(scenarios.func2), function(x) compute_scnR2(data.frame(scenarios.func2[x,])), future.seed=TRUE)
scenarios.func2$R2 <- round(scenarios.func2$R2,2)
plan(sequential)
xtabs(R2~eps.y+eps.g, data = scenarios.func2)
```


## Scenario: functional form = sine

```{r sine_l}
# --- Scenario: functional form
scenarios.func3 <- scenarios %>% filter(n==N & p==P  & dg.thresh == "sine" & setting == "latent" & outcome=="prognostic")
plan(multisession, workers=detectCores()*.75)
scenarios.func3$R2 <- future_sapply(1:nrow(scenarios.func3), function(x) compute_scnR2(data.frame(scenarios.func3[x,])), future.seed=TRUE)
scenarios.func3$R2 <- round(scenarios.func3$R2,2)
plan(sequential)
xtabs(R2~eps.y+eps.g, data = scenarios.func3)
```



# Setting: diagnostic

```{r single_l}
# --- Scenario: single threshold = 0.25
scenarios$R2 <- NA
scenarios.diag <- scenarios %>% filter(n==N & p==P & outcome=="diagnostic")

plan(multisession, workers=detectCores()*.75)
scenarios.diag$R2 <- future_sapply(1:nrow(scenarios.diag), function(x) compute_scnR2(scenarios.diag[x,]), future.seed=TRUE)
scenarios.diag$R2 <- round(scenarios.diag$R2,2)
plan(sequential)
xtabs(R2~eps.y+eps.g, data = scenarios.diag)
```
